Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-12 src/tex/ms.tex
disentangle fluxes

The goal of this work is to evaluate the potential of future exoplanet surveys to test the hypothesis that a minimum past \gls{NUV} flux is required for abiogenesis.
We focus on one version of the UV Threshold Hypothesis, the so-called cyanosulfidic scenario, which has been refined to the point where the required threshold flux has been measured \rev{to be $\SI{6.8\pm3.6 e10}{\photons\per\centi\meter\squared\per\second\per\nano\meter}$ integrated} from \SIrange{200}{280}{\nano\meter} at the surface~\citep{Rimmer2018,Rimmer2021a,Rimmer2023,Ranjan2023a}.
%\todo[inline]{SR: This is an interesting number, because it is below what was available on early Earth (so this scenario could have worked on early Earth) but until recently it was below what was thought to be available on \gls{HZ} M-dwarf exoplanets. So it was thought that identification of biosignatures on M-dwarf planets could therefore falsify the cyanosulfidic scenario, with a potential caveat for transient UV from flares. Two recent developments have complicated the picture. First, Rimmer et al. 2018 had an error in their radiative transfer routines. Correcting for this error, early M-dwarfs and highly active M-dwarfs emit enough UV to meet the Rimmer et al. 2018 criterion (Ranjan et al. 2023).
%\sout{Second, a recent publication argues that /all/ estimates of M-dwarf UV are underestimates, and that late M-dwarf stars have similar emission to Sunlike stars (Rekhi et al. 2023). I suspect this is incorrect, because it contradicts a lot of work from e.g. the MUSCLES collaboration and the HAZMAT project, but it's worth keeping an eye on in case it is correct after all.}}
\rev{While prebiotic photochemistry is fundamentally driven by photon number flux, we choose to frame the problem in terms of energy flux, for which empirical estimates in the \gls{NUV} exist across stellar populations and ages~\citep{Richey-Yowell2023}.
In these units, the above threshold is approximately \var{rimmer_threshold}$\pm$\var{rimmer_uncertainty}$\,$\SI{}{\erg\per\second\per\centi\meter\squared}.
However, due to uncertainties in how surface flux relates to top-of-atmosphere flux in the habitable zone, we treat the threshold \gls{NUV} flux as a free parameter.}

>>>>

The goal of this work is to evaluate the potential of future exoplanet surveys to test the hypothesis that a minimum past \gls{NUV} flux is required for abiogenesis.
We focus on one version of the UV Threshold Hypothesis, the so-called cyanosulfidic scenario, which has been refined to the point where the required threshold flux has been measured \rev{to be $\SI{6.8\pm3.6 e10}{\photons\per\centi\meter\squared\per\second\per\nano\meter}$ integrated} from \SIrange{200}{280}{\nano\meter} at the surface~\citep{Rimmer2018,Rimmer2021a,Rimmer2023,Ranjan2023a}\rev{\footnote{or $\sim$\var{rimmer_threshold}$\pm$\var{rimmer_uncertainty}$\,$\SI{}{\erg\per\second\per\centi\meter\squared} in energy flux units.}}.
\rev{While prebiotic photochemistry is fundamentally driven by photon number flux, we choose to frame the problem in terms of energy flux, for which empirical estimates in the \gls{NUV} exist across stellar populations and ages~\citep{Richey-Yowell2023}.
Due to the inherent uncertainties concerning the relationship between surface and top-of-atmosphere fluxes, we treat the threshold \gls{NUV} flux as a free parameter.}
